Towards a Complete Model of the Negative Selection Process in Humans

### 2023-05-24 manuscript/manuscript.tex
local fig AI stuff
new figures, captions

\begin{figure}[!htb]
  \centering
  \includegraphics{figures/figure1.pdf}
  \caption{}
  \label{fig:figure-1}
\end{figure}

>>>>

\begin{figure}[htbp]
  \centering
  \includegraphics[width=\textwidth]{figures/figure_1.pdf}
  \caption{Theory compared to simulation results. (A) The predicted reduction
      factor under classic B theory (dark gray line) and the diploid SC16 model
      (colored lines corresponding to mutation rate) compared to average
      reduction across XXX simulation replicates (points). (B) The predicted
      ratchet rate under the SC16 model scaled by mutation rate (colored lines)
      compared to the ratchet estimated from simulation (points). When $2Ns>1$,
      the ratchet rate is near zero. (C) The genic variance from simulations
      (points) against the predicted variance under the SC16 model (colored
      lines). As the ratchet begins to click, the genic variance is decreased
      from the level expected under strong BGS (dashed line). (D, bottom) The
      mean squared error (MSE) between whole-chromosome simulations and
      predicted classic B (dots), new B' (solid), and locally-rescaled B'
      (dashed) for different mutation rates (colors). The dashed horizontal
      line is the approximate theoretic minimum MSE  (D, top) The build up of
      negative linkage disequilibria around $2Ns=1$ in whole-chromosome
      simulations. (E) The average B across 100 chromosome 10 simulation
  replicates (gray) against different predictions, for parameters that
correspond to $2Ns < 1$, $2Ns = 1$, and $2Ns > 1$. }
  \label{fig:figure-1}
\end{figure}
